### 2019-02-22 Sections/economics_of_the_quantum_internet.tex
Coll enh fig

This is easily intuitively seen as follows. Let the computational scaling function be an arbitrary exponential,\index{Multiplicativity in computational power}
\begin{align}
f_\mathrm{sc}(n) = O(\mathrm{exp}(n)).	
\end{align}
Then it immediately follows that the scaling function obeys the identity,
\begin{align}
	f_\mathrm{sc}\left(\sum_i n_i \right) = \prod_i f_\mathrm{sc}(n_i),
\end{align}
yielding the multiplicative behaviour.

>>>>

This is easily intuitively seen as follows. Let the computational scaling function be an arbitrary exponential,\index{Multiplicativity in computational power}
\begin{align}
f_\mathrm{sc}(n) = O(\mathrm{exp}(n)).	
\end{align}
Then it immediately follows that the scaling function obeys the identity,
\begin{align}\label{eq:prod_comp_sc}
	f_\mathrm{sc}\left(\sum_i n_i \right) = \prod_i f_\mathrm{sc}(n_i),
\end{align}
yielding the multiplicative behaviour, shown diagrammatically in the context of a distributed quantum computation in Fig.~\ref{fig:exp_coll_enh}. Note that in the classical case the product in Eq.~(\ref{eq:prod_comp_sc}) would be become a sum, which is exponentially smaller in generally,
\begin{align}
	\prod_i f_\mathrm{sc}(n_i) \geq \sum_i f_\mathrm{sc}(n_i).
\end{align}

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{collective_enhancement}
\captionspacefig \caption{A distributed quantum computation across a number of nodes, each with $n_i$ qubits. The computational scaling function is chosen to be exponential in form,  yielding a classical-equivalent computational power of \mbox{$\mathrm{exp}(n_i)$} for each node. However, the joint computational power of the network is given by \mbox{$\mathrm{exp}(n_1+n_2+\dots)$}, which is exponentially greater than the sum of the individual computational powers, \mbox{$\mathrm{exp}(n_1)+\mathrm{exp}(n_2)+\dots$}, in general.}\label{fig:exp_coll_enh}
\end{figure}
